### 2016-11-05 conclusions.tex
saturday more shit

\section{Conclusions \& Future Work}
%\subsection{Conclusions}
Pruning neurons (instead of pruning individual weights) in a pre-trained neural network without seeing a major loss in performance is not only possible but also enables compressing networks to 40-70\% of their original size, which is of great importance in constrained memory environments like embedded devices. This fact is established through the experiments using the brute force criterion, which if made computationally viable (through parallelization) or approximated more efficiently than the Taylor Series based methods discussed in this paper, can prove to be a useful compression tool. It would also be interesting to see how these methods perform on deeper networks and on some other popular and real world datasets. Also, as mentioned in Section \ref{sec2}, we have not considered all possible combinations of neuron interdependence in this work due to the in-feasibility of implementation and have always pruned one neuron at a time. Even though the greedy evaluation of such combinations is highly prohibitive, it is not entirely implausible to think that algorithms can be developed for it in the future. That would help in truly tapping into the power of these interconnections and hopefully lead to impressive performance results.

The experiments on the visualization of error surfaces and pruning decisions concretely establish the fact that not all neurons in a network contribute to its performance in the same way. This confirms the idea put forth by \cite{mozer1989using} that learning representation is not distributed uniformly across neurons. Neural networks use a few neurons to learn the function approximation, and the remaining neurons cooperate to cancel out each other's effects. This is also a strong indication of the fact that once training is done, bigger networks do not hold an advantage over smaller ones, which is similar to the idea put forth by \cite{darkknowledge2015} in their work on ensemble learning techniques.

%It might also be interesting to see if the Cascade Correlation architecture arrives at the same number of final neurons as the pruning technique discussed in this paper.

>>>>

\section{Conclusions \& Future Work}
In conclusion, we must first re-assert that we do not present this work as a bench-marking study of the algorithm we derived and tested. We have merely used this algorithm as a jumping off point to investigate the nature of learning representations in neural networks. What we discovered is that first and second order methods do not make particularly good pruning decisions, and that a brute-force algorithm does surprisingly well, despite being computationally expensive. A simplistic brute-force method does so well in fact, we argue that further investigation is required to make this algorithm computationally tractable. We also observed strong evidence for the hypotheses of \cite{mozer1989skeletonization} regarding the dualist nature of neurons, i.e. that learning representations are divided between units which either participate in the output approximation or learn to cancel each others influence. This suggests that neural networks may in fact learn a minimal network implicitly, though we cannot say for sure that this is the case without further investigation. A necessary experiment in this vein would be to compare the size of network constructed using cascade correlation and compare it to the results described herein.

We have presented a novel algorithm for pruning whole neurons from a trained neural network using a second-order Taylor series approximation of the change in error resulting from the removal a given neuron as a pruning criteria. We compared this method to a first order method and a brute-force serial removal method which exhaustively found the next best single neuron to remove at each stage. Our algorithm relies on a combination of assumptions similar to the ones made by \cite{mozer1989skeletonization} and \cite{lecun1989optimal} in the formulation of the Skeletonization and Optimal Brain Damage algorithms. First, we assumed that the error function with respect to each individual neuron can be approximated with a straight line or more precisely with a parabola. Second, for second derivative terms we consider only the diagonal elements of the Hessian matrix, i.e. we assume that each neuron-weight connection can be treated independently of the other elements in the network. Third, we assumed that pruning could be done in a serial fashion in which we find the single least productive element in the network, remove it, and move on. We found that all of these assumptions are deeply flawed in the sense that the true relevance of a neuron can only be partially approximated by a first or second order method, and only at certain stages of the pruning process. For most problems, these methods can usually remove between 10-30\% of the neurons in a trained network, but beyond this point their reliability breaks down. For certain problems, none of the described methods seem to perform very well, though for obvious reasons the brute-force method always exhibits the best results. The reason for this is that the error function with respect to each hidden unit is more complex than a simple second-order Taylor series can approximate. Furthermore, we have not directly taken into account the interdependence of elements within a network, though the work of \cite{hassibi1993second} could provide some guidance in this regard. This is another critical issue to investigate in the future.

Re-training may help in this regard. We freely admit that our algorithm does not use re-training to recover from errors made in pruning decisions. We argue that evaluating a network pruning algorithm using re-training does not allow us to make fair comparisons between the kinds of decisions made by these algorithms. Neural networks are very good at recovering from the removal of individual elements with re-training and so this compensates for sub-optimal pruning criteria.

We have observed that pruning whole neurons from an optimally trained network without major loss in performance is not only possible but also enables compressing networks to 40-70\% of their original size, which is of great importance in constrained memory environments like embedded devices. We cite the results of our experiments using the brute force criterion as evidence of this conclusion. However expensive, it would be extremely easy to parallelize this method, or potentially approximate it using a subset of the training data to decide which neurons to prune. This avoids the problem of trying to approximate the importance of a unit and potentially making a mistake.

It would also be interesting to see how these methods perform on deeper networks and on some other popular and real world datasets. In our case, on the MNIST dataset, we observed that it was more difficult to prune neurons from a deeper network than from one with a single layer. We should expect this trend to continue as networks get deeper and deeper, which also calls into further question the reliability of the described first and second order methods. We did investigate the order in which neurons were plucked from each layer of the networks and we found that the brute force method primarily removes neurons from the deepest layer of the network first, but there was no obvious pattern in layer preference for the other two methods.

Our experiments using the visualization of error surfaces and pruning decisions concretely establish the fact that not all neurons in a network contribute to its performance in the same way, and the observed complexity of these functions demonstrates limitations of the approximations we used.

Finally, we encourage the readers of this work to take these results into consideration when making decisions as to which methods to use to improve network generalization or compress their models. It should be remembered that various heuristics may perform well in practice for reasons which are in fact orthogonal to the accepted justifications given by their proponents.
